Variation in distance between consecutive animal locations

### 2021-03-19 distributions_paper/r2n_rudolph_distributions.Rmd
distributions

# focus <- "dist"
# focus <- "R2n"
 focus <- "mpm"
# focus <- "m15"

@@

if(focus == "R2n"){
  df <- aracari_df %>%
  dplyr::filter(R2n != 0) %>%
  group_by(id) %>%
  filter(., n() >= 30) %>%
  ungroup() %>%
  dplyr::filter(R2n != 0) %>% 
    mutate(Bird_ID = paste0("B", id),
           focus = sqrt(R2n))

>>>>

# focus <- "dist"
 focus <- "R2n"
# focus <- "mpm"
# focus <- "m15"

@@

if(focus == "R2n"){

  df <- aracari_df %>%
    mutate(R2n = lead(R2n)) %>% 
    dplyr::filter(R2n != 0) %>%
    group_by(id) %>%
    filter(., n() >= 30) %>%
    ungroup() %>%
    dplyr::filter(R2n != 0) %>% 
    mutate(Bird_ID = paste0("B", id),
           tmin = dt/60)
